A Large-Scale Study of the Use of Eval in R

### 2020-08-27 inst/paper/main.tex
Add side-effect data

\input{tag/counts.tex}
\input{tag/corpus.tex}
\input{tag/analysisStable.tex}
\input{tag/enrichDataset.tex}

@@

>>>>

\input{tag/counts.tex}
\input{tag/corpus.tex}
\input{tag/side-effects.tex}
\input{tag/analysisStable.tex}
\input{tag/enrichDataset.tex}

@@

\section{Side-Effects}

In the corpus we observe \AllWritesRnd writes to variables of which
\EvalWritesRnd writes happen inside \eval. However, all writes are not
dangerous. Only writes to environments not local to the computation spawned
by \eval are side-effecting. These writes outlive the computation and hence are
visible outside the computation. The remaining writes are local to the
computation. We observe that \EvalSideEffectingWritesRnd writes inside evals are
side-effecting. This is only \EvalSideEffectingWritesEvalPerc of all variable
writes inside \eval and \EvalSideEffectingWritesAllPerc of all variable writes
in the corpus.

An \eval is considered side-effecting if it performs a side-effecting write to a
variable, directly or indirectly. Only \SideEffectingCoreCallPerc \eval calls in
Core R are side-effecting and \SideEffectingPackageCallPerc \eval calls in CRAN
packages are side-effecting.
